Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-03-18 analysis/paper/paper.Rmd
first figs

pots<-read.csv("../data/raw_data/KnossosPots.csv",header=T)

ggplot(pots,aes(pots$ave_date))+geom_histogram()+xlim(1100,600)
```

>>>>

allpots<-read.csv("../data/raw_data/KnossosPots.csv",header=T)
pots<-subset(allpots,cemetery=="NC"|cemetery=="FOR"|cemetery=="TK")
potsnop<-subset(allpots,tomb!="P")
str(pots)

allpots$tomb_period<- factor(allpots$tomb_period, levels = c("SM", "EPG", "MPG", "PG","LPG","PGB","EG","MG","G","LG",
                                                       "EO","O","LO",""))

ggplot(pots,aes(pots$ave_date,fill=tomb_period,color=tomb_period))+geom_histogram()+xlim(1100,600)
ggplot(tombp,aes(tombp$ave_date,fill=period,color=period))+geom_histogram()+xlim(1100,600)
```
